Title

### 2023-04-12 main.tex
I'm guessing this may start causing us problems either soon or never.

% Template for PLoS
% Version 3.6 Aug 2022
%
% % % % % % % % % % % % % % % % % % % % % %
%
% -- IMPORTANT NOTE
%
% This template contains comments intended 
% to minimize problems and delays during our production 
% process. Please follow the template instructions
% whenever possible.
%
% % % % % % % % % % % % % % % % % % % % % % % 
%
% Once your paper is accepted for publication, 
% PLEASE REMOVE ALL TRACKED CHANGES in this file 
% and leave only the final text of your manuscript. 
% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
%
%
% There are no restrictions on package use within the LaTeX files except that no packages listed in the template may be deleted.
%
% Please do not include colors or graphics in the text.
%
% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
%
% % % % % % % % % % % % % % % % % % % % % % %
%
% -- FIGURES AND TABLES
%
% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
%
% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
% - Figures should be uploaded separately from your manuscript file. 
% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
% For figure citations, please use "Fig" instead of "Figure".
% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
%
% Tables should be cell-based and may not contain:
% - spacing/line breaks within cells to alter layout or alignment
% - do not nest tabular environments (no tabular environments within tabular environments)
% - no graphics or colored text (cell background color/shading OK)
% See http://journals.plos.org/plosone/s/tables for table guidelines.
%
% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
%
% % % % % % % % % % % % % % % % % % % % % % % %
%
% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
%
% IMPORTANT
% Below are a few tips to help format your equations and other special characters according to our specifications. For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
%
% For inline equations, please be sure to include all portions of an equation in the math environment.  For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
%
% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
%
% Please add line breaks to long display equations when possible in order to fit size of the column. 
%
% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
%
% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2". 
%
% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
%
% % % % % % % % % % % % % % % % % % % % % % % % 
%
% Please contact latex@plos.org with any questions.
%
% % % % % % % % % % % % % % % % % % % % % % % %

\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}

% amsmath and amssymb packages, useful for mathematical formulas and symbols
\usepackage{amsmath,amssymb}

% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{changepage}

@@

\begin{document}
\vspace*{0.2in}

@@

% Use "Eq" instead of "Equation" for equation citations.
\section*{Introduction}
%Lorem ipsum dolor sit~\cite{bib1} amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam Eq~(\ref{eq:schemeP}) sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id.%~\cite{bib2} Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.

\begin{eqnarray}
\label{eq:schemeP}
	\mathrm{P_Y} = \underbrace{H(Y_n) - H(Y_n|\mathbf{V}^{Y}_{n})}_{S_Y} + \underbrace{H(Y_n|\mathbf{V}^{Y}_{n})- H(Y_n|\mathbf{V}^{X,Y}_{n})}_{T_{X\rightarrow Y}},
\end{eqnarray}

\section*{Circuits for Pauli Maps}
\label{sec: Circuits for Pauli Maps}

\textbf{Lista de puntos:}
\begin{itemize}
\item \textbf{Circuit for a Pauli channel:}  Propose a circuit to simulate a Pauli channel on $n$ qubits. It works by creating a $2n$-qubit state on ancilla qubits.
\item \textbf{Simulation:} Show the fidelities of simulating the circuit on a quantum computer for many one-qubit channels inside the tetrahedron.
\item \textbf{For Pauli dynamical maps}: See how the circuit generalizes to parametrized channels and notice that many rotations are needed to create the $2n$-ancilla qubit state. \\
\end{itemize}

In this section we introduce the concept of Pauli channels and 
Pauli dynamical maps, as well as proposal for a quantum circuit that simulates them on systems of $N$ qubits. 
Furthermore, we show the results of implementing the circuit on a 
quantum computer for the particular case of Pauli channels of one qubit.

\subsection*{Quantum Channels}
\label{subsec: Quantum Channels}
Quantum channels are the most general linear operations that a 
quantum system (which is represented by a density matrix $\rho$) 
can undergo independently of its past~\cite{zimansbook,cirac}. 
These channels are constructed based on three fundamental properties: 
linearity, trace preservation, and complete positivity.

@@

\subsection*{Pauli Channels}
\label{subsec: Pauli Channels}

To define a Pauli channel, we start by exploring the single-qubit scenario and then the $N$-qubit one. 
First of all, the most general single-qubit density matrix can be written as
\begin{eqnarray}
\label{ec: Density Matrix}
\rho = \dfrac{1}{2} \sum_{\alpha=0}^{3} r_{\alpha} \sigma_{\alpha},
\end{eqnarray}
with $\sigma_0 = \mathbb{I}$, and $\sigma_{1,2,3}$ the usual Pauli matrices. 
Normalization requires that $r_0 = 1$ and the remaining $r_{1,2,3}$ form a Bloch vector. 
A Pauli channel is defined as an operation
that applies a convex combination of Pauli matrices to the density matrix in the following way:
\begin{eqnarray}
\label{ec: Pauli channel 1 qbit}
\mathcal{E}(\rho) = \sum_{\gamma=0}^3 k_{\gamma} \sigma_{\gamma} \rho \sigma_{\gamma},
\end{eqnarray}
where $k_{\gamma}$ are non-negative real numbers such that 
$\sum_{\gamma} k_{\gamma} = 1$ (these conditions are needed for the channel 
to be completely positive and trace preserving).

@@

\subsection*{Circuit for a Pauli Channel}
\label{subsec: Circuit for a Pauli Channel}

@@

\begin{figure}[h!]
\centering
\begin{quantikz}
\lstick{$q_0$} & \qw & \qw & \qw & \gate{\sigma_{\gamma_0}} & \qw & & &  & & \rstick[wires=12]{Repeat for all \\
 vectors $\vec{\gamma}$} \\
\lstick{$q_1$} & \qw & \qw & \qw & \gate{\sigma_{\gamma_1}} & \qw & & & &\\
\lstick{ } & \vdots & \vdots & \vdots & &  & & & &\\
\lstick{$q_{n-1}$} & \qw & \qw & \qw & \gate{\sigma_{\gamma_{n-1}}} & \qw & & &\\
\lstick{ } & & & & & &\\
\lstick{$aq_0$} & \qw & \gate[wires=7,nwires=5]{\text{Create the $2N$ qubits state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}   |\vec{\gamma} \rangle$}} & \qw &  \ctrl{-5} & \qw & \rstick[wires=2]{$|\gamma_0 \rangle$} &  & & &\\
\lstick{$aq_1$} & \qw & & \qw &  \ctrl{-6} &\qw & & & & & \\
\lstick{$aq_2$} &\qw & & \qw &  \ctrl{-7} & \qw & \rstick[wires=2]{$|\gamma_1 \rangle$} & & & &\\
\lstick{$aq_3$} &\qw & & \qw &  \ctrl{-8} & \qw & & & & &\\
\vdots  &\vdots & & \vdots & &  \vdots & & & & &\\
\lstick{$aq_{2N-2}$}& \qw &  &\qw  & \ctrl{-10} & \qw & \rstick[wires=2]{$|\gamma_{n-1} \rangle$}& & & & \\
\lstick{$aq_{2N-1}$}& \qw & & \qw  &  \ctrl{-11} & \qw & & & & &\\
\end{quantikz}
\caption{\textbf{\tbnote{Hay que quitar esta imagen del texto al entregar el artículo y ponerla en un archivo a parte de tipo TIFF or EPS. Hay que dejar el figure solamente con la caption y label.}} {\bf Circuit for an $N$-qubit Pauli channel.} Circuit to implement an $N$-qubit Pauli channel 
on the qubits $q_0, q_1, \cdots, q_{n-1}$. 
The circuit creates the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}|\vec{\gamma}\rangle$ 
on $2N$ ancilla qubits and then uses them to apply
all possible Pauli strings on the principal qubits
with probabilities $k_{\vec{\gamma}}$.}
\label{fig: circuit-pauli}
\end{figure}

@@

\subsubsection*{Simulation for one-qubit Pauli channels}
\label{subsec: Simulation for one-qubit Pauli channels}
For the particular case of a Pauli channel on one qubit, 
the circuit that simulates it can be constructed as in Fig~(\ref{fig: citcuit-pauli-1}),
 which is a special case of Fig(\ref{fig: circuit-pauli}).

\begin{figure}[h!]
\centering
\begin{quantikz}
\lstick{$q_0$} & \qw & \gate{\sigma_1} & \gate{\sigma_2} & \gate{\sigma_3} & \qw \\
\lstick{$aq_0$} & \gate[wires=2][3cm]{\quad\quad \text{Create the two qubits state}\quad\quad} & \octrl{-1} & \ctrl{-1} & \ctrl{-1} & \qw \\
\lstick{$aq_1$} & \gateinput{$b_0 |0 \rangle |0 \rangle + b_1 |0 \rangle |1 \rangle + b_2 |1 \rangle |0 \rangle + b_3 |1 \rangle |1 \rangle $} & \ctrl{-2} & \octrl{-2}  & \ctrl{-2} & \qw
\end{quantikz}
\caption{\tbnote{Al igual que antes, hay que adaptar esta figura y quitarla antes de entregar}. {\bf One qubit Pauli channel circuit.} Circuit for a one-qubit Pauli channel, which is a particular case of Fig~(\ref{fig: circuit-pauli}).}
\label{fig: citcuit-pauli-1} 
\end{figure}
Taking advantage of the quantum computers that IBM has available,
we sampled $250$ one-qubit Pauli channels and simulated them using the 
ibmq-lima quantum computer. 
For each of these channels, the accuracy of the implementation in the quantum computer
was quantified by calculating the
 process fidelity of the Choi matrix obtained by performing
quantum process tomography to the circuit
with respect to the theoretical Choi matrix of
the corresponding channel.
Finally, using the well known fact that one-qubit Pauli channels can be represented
as points in a tetrahedron with corners $(1,1,1), (1-1,-1), (-1,1,-1)$ and $(-1,-1,1)$, 
in Fig~(\ref{fig: fidelity one qubit}).
\begin{figure}[h!]
\centering
\includegraphics[width=0.45\textwidth]{fidelity-points.png}\\
\caption{\tbnote{Al igual que antes, hay que quitar esta figura y ponerla en un archivo a parte}. {\bf Fidelities one-qubit Pauli channel} Fidelities of one-qubit Pauli channels implemented on IBM's ibmq-lima. The channels are plotted in the tetrahedron of Pauli channels, with a color bar indicating the fidelity of each channel's implementation using the circuit for a 1-qubit Pauli channel}
\label{fig: fidelity one qubit}
\end{figure}

\subsubsection*{Pauli Dynamical Maps}
\label{subsec: Pauli Dynamical Maps}

@@

Dynamical maps can be implemented using the same circuit as 
in Fig~(\ref{fig: circuit-pauli}), with the only difference that now the state 
to be created on the ancilla qubits depends on parameter $p$ 
and therefore is given by 
\begin{eqnarray}
\label{ec: parametrized state}
\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle.
\end{eqnarray}

\section*{OPR Circuits}
\label{sec: OPR Circuits}
\textbf{Puntos:}
\begin{itemize}
\item As said before, to implement a Pauli dynamical map, 
we need to create the parametrized $2n$-qubit state 
$\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle$ on the ancilla qubits.
\item However, creating this state will in general require many rotations parametrized by $p$. 
For example, for the case of a Pauli dynamical map on 1 qubit, 
the parametrized state of the $2$ ancilla qubits in general requires $3$ parametrized rotations and can be constructed as follows: (poner circuito).\\
In general, to create a parametrized state on $2n$ ancilla qubits will require
$2n-1$ rotations parametrized by $p$.
\item How can we reduce the amount of parametrized rotations used?
\item \textbf{OPR Circuit:} Define an OPR circuit (a circuit with one parametrized rotation)
\item \textbf{Theorem about OPR circuits:} \textit{An OPR circuit on $n$ qubits with parameter $p$ always has an operator of the form:}
\begin{eqnarray}
U = (\vec{v}_0| \vec{v}_1| \cdots| \vec{v}_{2^n-1})
\end{eqnarray}
\textit{where $s = s(p)$ and the column vectors are $\vec{v}_j = e^{is} \vec{a}_j + e^{-is} \vec{b}_j + \vec{c}_j$, with $\vec{a}_j, \vec{b}_j, \vec{c}_j$ orthogonal vectors and $|\vec{a}_j|^2 + |\vec{b}_j|^2 + |\vec{c}_j|^2 = 1$.}
\item \textbf{Proof:} La prueba está dentro de las ``Cosas-Escritas-Antes'', 
aunque se puede y debe achicar bastante.
\end{itemize}

\section*{OPR circuit for a Pauli map}
\label{sec: OPR circuit for a Pauli map}
\textbf{Puntos:}
\begin{itemize}
\item Use the last theorem to conclude directly which maps can be created using an OPR circuit.
\item \textbf{Examples:} Show examples that satisfy these conditions: Bit-Flip, parabolic maps, etc. 
and an example that doesn't satisfy the conditions (ejemplo está en la tesis).
\item \textbf{Results:} Show results of simulating those maps on a quantum computer. 
Lo tengo para parabolic y para depolarizing.
\end{itemize}

\section*{Exponential maps $e^{iHt}$}
\label{sec: Exponential maps}
\textbf{Puntos:}

\begin{itemize}
\item We will apply the results about OPR circuit to another kind of operation, those given by $U  = e^{iHt}$ where $H$ is hermitian  and time independent.
\item \textbf{Lemma:}\textit{ The $n$-qubit operator $U^{iHt}$ can be implemented with an OPR circuit of $n$ qubits if and only if $D = \text{diag}(e^{i\lambda_0 t}, \cdots, e^{i \lambda_{2^n-1}t})$ can be implemented with an OPR circuit of $n$ qubits, where $\lambda_j$ are the eigenvalues of $H$.}
\item \textbf{Proof:}  Es b\'asicamente usar que $H = QDQ^{-1}$ para una matriz $Q$ que no depende de $t$ y por lo tanto no agrega compuertas parametrizadas al circuito. 
\item \textbf{Theorem:} \textit{ A n-qubit operator of the form $U = e^{iHt}$ can be implemented using an OPR circuit if and only if the eigenvalues of $H$ are $-\lambda,0,\lambda$ (for $\lambda$ a real number) and the degeneracies of $\lambda$ and $-\lambda$ are both equal to $2^j$ for some $j\in \{0,1,\cdots,n-1\}$.}
\item \textbf{Proof:} Estoy buscando formas de simplificar la prueba, porque es medio larguita. Pero básicamente es usar el lema y entonces preocuparnos sólo por $D$. Luego  usar el teorema de la sección 3 y notar que sólo hay tres tipos de  $\lambda$s posibles y luego notar que deben de tener esas degeneraciones.
\item \textbf{Proof del regreso:} Aquí quiero recalcar que la prueba es constructiva, ya que consiste en mostrar cómo construir el circuito OPR que hace la operación a partir de una $H$ que cumpla la hipótesis. 
\item \textbf{Examples.} Mencionar que por el teorema, los ejemplos son sistemas con 3 energías separadas por la misma distancia y con las degeneraciones dadas en el teorema. 
La verdad que no se me ocurren sistemas físicos comunes que cumplan eso.
\begin{itemize}
\item Cualquier matriz $H$ de un qubit cumple el teorema.
\item Cualquier matriz de $n$ qubits que sea el producto tensorial de matrices de Pauli para cada partícula (o sea algo como $\sigma_{i_1} \otimes \sigma_{i_2} \otimes \cdots \otimes \sigma_{i_n}$) cumple el teorema.
\item Estoy viendo para cadenas de espines si hay condiciones para las que cumplan las hipótesis del teorema, pero no he encontrado aún.
\end{itemize}
\item Hice explícitamente el circuito de 2 qubits para $H = \sigma_3 \otimes \sigma_2$ y lo simulé en las computadoras de IBM, obteniendo una fidelidad de $0.85$.
\end{itemize}

\section*{Conclusion}

@@

Sed non aliquet felis. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Mauris commodo justo ac dui pretium imperdiet. Sed suscipit iaculis mi at feugiat. Ut neque ipsum, luctus id lacus ut, laoreet scelerisque urna. Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed. Nam condimentum sem eget mollis euismod. Nullam dui urna, gravida venenatis dui et, tincidunt sodales ex. Nunc est dui, sodales sed mauris nec, auctor sagittis leo. Aliquam tincidunt, ex in facilisis elementum, libero lectus luctus est, non vulputate nisl augue at dolor. For more information, see \nameref{S1_Appendix}.

\section*{Supporting information}

>>>>

\documentclass[10pt,letterpaper]{article} % {{{
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
\usepackage{amsmath,amssymb}
% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{changepage}

@@

% }}}
\begin{document}
% Titulo, afiliacion, abstract  {{{
\vspace*{0.2in}

@@

% Use "Eq" instead of "Equation" for equation citations.
% }}}
\section*{Introduction} % {{{
%Lorem ipsum dolor sit~\cite{bib1} amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam Eq~(\ref{eq:schemeP}) sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id.%~\cite{bib2} Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.

\begin{eqnarray}
\label{eq:schemeP}
	\mathrm{P_Y} = \underbrace{H(Y_n) - H(Y_n|\mathbf{V}^{Y}_{n})}_{S_Y} + \underbrace{H(Y_n|\mathbf{V}^{Y}_{n})- H(Y_n|\mathbf{V}^{X,Y}_{n})}_{T_{X\rightarrow Y}},
\end{eqnarray}
% }}}
\section{Circuits for Pauli Maps}  \label{sec: Circuits for Pauli Maps} % {{{
% Intro  {{{
\textbf{Lista de puntos:}
\begin{itemize}
\item \textbf{Circuit for a Pauli channel:}  Propose a circuit to simulate a Pauli channel on $n$ qubits. It works by creating a $2n$-qubit state on ancilla qubits.
\item \textbf{Simulation:} Show the fidelities of simulating the circuit on a quantum computer for many one-qubit channels inside the tetrahedron.
\item \textbf{For Pauli dynamical maps}: See how the circuit generalizes to parametrized channels and notice that many rotations are needed to create the $2n$-ancilla qubit state. \\
\end{itemize}

In this section \cpnote{ser coherente con las subsecciones que se tienen nota que no 
hay mencion a los quantum channels. Menos
cuadrado, quizá pasar por chatgpt. hacerlo al final cuanod se tenga el capitulo
por lo menos leido y aprobado en principio de mi parte.} we introduce the
concept of Pauli channels and Pauli dynamical
maps, as well as proposal for a quantum circuit that simulates them on systems
of $N$ qubits.  Furthermore, we show the results of implementing the circuit on
a quantum computer for the particular case of Pauli channels of one qubit. 
% }}}
\subsection*{Quantum Channels} \label{subsec: Quantum Channels} % {{{

\cpnote{Creo que toca iterar, pensando un poco en nivel licenciatura. ver ejemplos }
\cpnote{Tambien creo que no es coherente tener una subseccion para esto si 
lo qeu se quiere decir en la seccion es otra cosa.}

Quantum channels are the most general linear operations that a 
quantum system (which is represented by a density matrix $\rho$) 
can undergo independently of its past~\cite{zimansbook,cirac}. 
These channels are constructed based on three fundamental properties: 
linearity, trace preservation, and complete positivity.

@@

% }}}
\subsection*{Pauli Channels} \label{subsec: Pauli Channels} % {{{

To define a Pauli channel, we start by exploring the single-qubit scenario and
then the $N$-qubit one.  First of all, the most general single-qubit density
matrix can be written as
\begin{eqnarray}
\label{ec: Density Matrix}
\rho = \dfrac{1}{2} \sum_{\alpha=0}^{3} r_{\alpha} \sigma_{\alpha},
\end{eqnarray}
with $\sigma_0 = \mathbb{I}$, and $\sigma_{1,2,3}$ the usual Pauli matrices.
Normalization requires that $r_0 = 1$ and the remaining $r_{1,2,3}$ form a
Bloch vector \cpnote{explicar un poco mejor. Me parece que para el publico vale 
la pena ser un poco mas explicito. pero no estoy muy seguro. }. 
A Pauli channel is defined as an operation
that applies a convex combination of Pauli matrices to the density matrix in the following way:
\begin{eqnarray}
\label{ec: Pauli channel 1 qbit}
\mathcal{E}(\rho) = \sum_{\gamma=0}^3 k_{\gamma} \sigma_{\gamma} \rho \sigma_{\gamma},
\end{eqnarray}
where $k_{\gamma}$ are non-negative real numbers such that 
$\sum_{\gamma} k_{\gamma} = 1$ (these conditions are needed for the channel 
to be completely positive and trace preserving). 
\cpnote{en todo hay que mejorar un poco la redaccion. Aca me gustaria que 
se interpretara. Creo qe es mas que atenuacion de los componentes, o es solo atenuacion? 
en todo caso ver mejor como va la cosa. }

@@

\cpnote{Creo qeu toca motivar, conectar con cosas conocidas y en general no ser tan seco}
% }}}
\subsection*{Circuit for a Pauli Channel} % {{{
\label{subsec: Circuit for a Pauli Channel}

\cpnote{esto está un poco desordenado y a un ritmo creo qeu inapropiado por lo rapido}

@@

\cpnote{paro aca de leer}

\begin{figure}[h!]
\centering
\begin{quantikz}
\lstick{$q_0$} & \qw & \qw & \qw & \gate{\sigma_{\gamma_0}} & \qw & & &  & & \rstick[wires=12]{Repeat for all \\
 vectors $\vec{\gamma}$} \\
\lstick{$q_1$} & \qw & \qw & \qw & \gate{\sigma_{\gamma_1}} & \qw & & & &\\
\lstick{ } & \vdots & \vdots & \vdots & &  & & & &\\
\lstick{$q_{n-1}$} & \qw & \qw & \qw & \gate{\sigma_{\gamma_{n-1} }} & \qw & & &\\
\lstick{ } & & & & & &\\
\lstick{$aq_0$} & \qw & \gate[wires=7,nwires=5]{\text{Create the $2N$ qubits state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}   |\vec{\gamma} \rangle$}} & \qw &  \ctrl{-5} & \qw & \rstick[wires=2]{$|\gamma_0 \rangle$} &  & & &\\
\lstick{$aq_1$} & \qw & & \qw &  \ctrl{-6} &\qw & & & & & \\
\lstick{$aq_2$} &\qw & & \qw &  \ctrl{-7} & \qw & \rstick[wires=2]{$|\gamma_1 \rangle$} & & & &\\
\lstick{$aq_3$} &\qw & & \qw &  \ctrl{-8} & \qw & & & & &\\
\vdots  &\vdots & & \vdots & &  \vdots & & & & &\\
\lstick{$aq_{2N-2}$}& \qw &  &\qw  & \ctrl{-10} & \qw & \rstick[wires=2]{$|\gamma_{n-1} \rangle$}& & & & \\
\lstick{$aq_{2N-1}$}& \qw & & \qw  &  \ctrl{-11} & \qw & & & & &\\
\end{quantikz}
\caption{\textbf{\tbnote{Hay que quitar esta imagen del texto al entregar el artículo y ponerla en un archivo a parte de tipo TIFF or EPS. Hay que dejar el figure solamente con la caption y label.}} {\bf Circuit for an $N$-qubit Pauli channel.} Circuit to implement an $N$-qubit Pauli channel 
on the qubits $q_0, q_1, \cdots, q_{n-1}$. 
The circuit creates the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}|\vec{\gamma}\rangle$ 
on $2N$ ancilla qubits and then uses them to apply
all possible Pauli strings on the principal qubits
with probabilities $k_{\vec{\gamma}}$.}
\label{fig: circuit-pauli}
\end{figure}

@@

\subsubsection*{Simulation for one-qubit Pauli channels} % {{{
\label{subsec: Simulation for one-qubit Pauli channels}
For the particular case of a Pauli channel on one qubit, 
the circuit that simulates it can be constructed as in Fig~(\ref{fig: citcuit-pauli-1}),
 which is a special case of Fig(\ref{fig: circuit-pauli}).

\begin{figure}[h!]
\centering
\begin{quantikz}
\lstick{$q_0$} & \qw & \gate{\sigma_1} & \gate{\sigma_2} & \gate{\sigma_3} & \qw \\
\lstick{$aq_0$} & \gate[wires=2][3cm]{\quad\quad \text{Create the two qubits state}\quad\quad} & \octrl{-1} & \ctrl{-1} & \ctrl{-1} & \qw \\
\lstick{$aq_1$} & \gateinput{$b_0 |0 \rangle |0 \rangle + b_1 |0 \rangle |1 \rangle + b_2 |1 \rangle |0 \rangle + b_3 |1 \rangle |1 \rangle $} & \ctrl{-2} & \octrl{-2}  & \ctrl{-2} & \qw
\end{quantikz}
\caption{\tbnote{Al igual que antes, hay que adaptar esta figura y quitarla antes de entregar}. {\bf One qubit Pauli channel circuit.} Circuit for a one-qubit Pauli channel, which is a particular case of Fig~(\ref{fig: circuit-pauli}).}
\label{fig: citcuit-pauli-1} 
\end{figure}
Taking advantage of the quantum computers that IBM has available,
we sampled $250$ one-qubit Pauli channels and simulated them using the 
ibmq-lima quantum computer. 
For each of these channels, the accuracy of the implementation in the quantum computer
was quantified by calculating the
 process fidelity of the Choi matrix obtained by performing
quantum process tomography to the circuit
with respect to the theoretical Choi matrix of
the corresponding channel.
Finally, using the well known fact that one-qubit Pauli channels can be represented
as points in a tetrahedron with corners $(1,1,1), (1-1,-1), (-1,1,-1)$ and $(-1,-1,1)$, 
in Fig~(\ref{fig: fidelity one qubit}).
\begin{figure}[h!]
\centering
\includegraphics[width=0.45\textwidth]{fidelity-points.png}\\
\caption{\tbnote{Al igual que antes, hay que quitar esta figura y ponerla en un archivo a parte}. {\bf Fidelities one-qubit Pauli channel} Fidelities of one-qubit Pauli channels implemented on IBM's ibmq-lima. The channels are plotted in the tetrahedron of Pauli channels, with a color bar indicating the fidelity of each channel's implementation using the circuit for a 1-qubit Pauli channel}
\label{fig: fidelity one qubit}
\end{figure}
% }}}
\subsubsection*{Pauli Dynamical Maps} % {{{
\label{subsec: Pauli Dynamical Maps}

@@

Dynamical maps can be implemented using the same circuit as 
in Fig~(\ref{fig: circuit-pauli}), with the only difference that now the state 
to be created on the ancilla qubits depends on parameter $p$ 
and therefore is given by 
\begin{eqnarray}
\label{ec: parametrized state}
\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle.
\end{eqnarray}
% }}}
% }}}
% }}}
\section*{OPR Circuits} % {{{
\label{sec: OPR Circuits}
\textbf{Puntos:}
\begin{itemize}
\item As said before, to implement a Pauli dynamical map, 
we need to create the parametrized $2n$-qubit state 
$\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle$ on the ancilla qubits.
\item However, creating this state will in general require many rotations parametrized by $p$. 
For example, for the case of a Pauli dynamical map on 1 qubit, 
the parametrized state of the $2$ ancilla qubits in general requires $3$ parametrized rotations and can be constructed as follows: (poner circuito).\\
In general, to create a parametrized state on $2n$ ancilla qubits will require
$2n-1$ rotations parametrized by $p$.
\item How can we reduce the amount of parametrized rotations used?
\item \textbf{OPR Circuit:} Define an OPR circuit (a circuit with one parametrized rotation)
\item \textbf{Theorem about OPR circuits:} \textit{An OPR circuit on $n$ qubits with parameter $p$ always has an operator of the form:}
\begin{eqnarray}
U = (\vec{v}_0| \vec{v}_1| \cdots| \vec{v}_{2^n-1})
\end{eqnarray}
\textit{where $s = s(p)$ and the column vectors are $\vec{v}_j = e^{is} \vec{a}_j + e^{-is} \vec{b}_j + \vec{c}_j$, with $\vec{a}_j, \vec{b}_j, \vec{c}_j$ orthogonal vectors and $|\vec{a}_j|^2 + |\vec{b}_j|^2 + |\vec{c}_j|^2 = 1$.}
\item \textbf{Proof:} La prueba está dentro de las ``Cosas-Escritas-Antes'', 
aunque se puede y debe achicar bastante.
\end{itemize}
% }}}
\section*{OPR circuit for a Pauli map} % {{{
\label{sec: OPR circuit for a Pauli map}
\textbf{Puntos:}
\begin{itemize}
\item Use the last theorem to conclude directly which maps can be created using an OPR circuit.
\item \textbf{Examples:} Show examples that satisfy these conditions: Bit-Flip, parabolic maps, etc. 
and an example that doesn't satisfy the conditions (ejemplo está en la tesis).
\item \textbf{Results:} Show results of simulating those maps on a quantum computer. 
Lo tengo para parabolic y para depolarizing.
\end{itemize}
% }}}
\section*{Exponential maps $e^{iHt}$} % {{{
\label{sec: Exponential maps}
\textbf{Puntos:}

\begin{itemize}
\item We will apply the results about OPR circuit to another kind of operation, those given by $U  = e^{iHt}$ where $H$ is hermitian  and time independent.
\item \textbf{Lemma:}\textit{ The $n$-qubit operator $U^{iHt}$ can be implemented with an OPR circuit of $n$ qubits if and only if $D = \text{diag}(e^{i\lambda_0 t}, \cdots, e^{i \lambda_{2^n-1}t})$ can be implemented with an OPR circuit of $n$ qubits, where $\lambda_j$ are the eigenvalues of $H$.}
\item \textbf{Proof:}  Es b\'asicamente usar que $H = QDQ^{-1}$ para una matriz $Q$ que no depende de $t$ y por lo tanto no agrega compuertas parametrizadas al circuito. 
\item \textbf{Theorem:} \textit{ A n-qubit operator of the form $U = e^{iHt}$ can be implemented using an OPR circuit if and only if the eigenvalues of $H$ are $-\lambda,0,\lambda$ (for $\lambda$ a real number) and the degeneracies of $\lambda$ and $-\lambda$ are both equal to $2^j$ for some $j\in \{0,1,\cdots,n-1\}$.}
\item \textbf{Proof:} Estoy buscando formas de simplificar la prueba, porque es medio larguita. Pero básicamente es usar el lema y entonces preocuparnos sólo por $D$. Luego  usar el teorema de la sección 3 y notar que sólo hay tres tipos de  $\lambda$s posibles y luego notar que deben de tener esas degeneraciones.
\item \textbf{Proof del regreso:} Aquí quiero recalcar que la prueba es constructiva, ya que consiste en mostrar cómo construir el circuito OPR que hace la operación a partir de una $H$ que cumpla la hipótesis. 
\item \textbf{Examples.} Mencionar que por el teorema, los ejemplos son sistemas con 3 energías separadas por la misma distancia y con las degeneraciones dadas en el teorema. 
La verdad que no se me ocurren sistemas físicos comunes que cumplan eso.
\begin{itemize}
\item Cualquier matriz $H$ de un qubit cumple el teorema.
\item Cualquier matriz de $n$ qubits que sea el producto tensorial de matrices de Pauli para cada partícula (o sea algo como $\sigma_{i_1} \otimes \sigma_{i_2} \otimes \cdots \otimes \sigma_{i_n}$) cumple el teorema.
\item Estoy viendo para cadenas de espines si hay condiciones para las que cumplan las hipótesis del teorema, pero no he encontrado aún.
\end{itemize}
\item Hice explícitamente el circuito de 2 qubits para $H = \sigma_3 \otimes \sigma_2$ y lo simulé en las computadoras de IBM, obteniendo una fidelidad de $0.85$.
\end{itemize}
% }}}
\section*{Conclusion} % {{{

@@

Sed non aliquet felis. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Mauris commodo justo ac dui pretium imperdiet. Sed suscipit iaculis mi at feugiat. Ut neque ipsum, luctus id lacus ut, laoreet scelerisque urna. Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed. Nam condimentum sem eget mollis euismod. Nullam dui urna, gravida venenatis dui et, tincidunt sodales ex. Nunc est dui, sodales sed mauris nec, auctor sagittis leo. Aliquam tincidunt, ex in facilisis elementum, libero lectus luctus est, non vulputate nisl augue at dolor. For more information, see \nameref{S1_Appendix}.
% }}}
\section*{Supporting information} % {{{
